### 2016-02-21 presentations/coda2016/coda2016_poster.tex
added manageable examples

%%-----------------------------------------------
%%
%%Top right box
%%
\begin{textblock}{14}(32.4, 5.71)
{\large \bfseries Manageable (a.k.a. small) examples} \\[.25cm]

As the magnitude of $\boldsymbol \theta$ grows, so does the occurence of near-degeneracy, instability, and uninterpretability for RBMs of varying sizes.

%%-----------------------------------------------
%%
%%Middle right box
%%
\begin{textblock}{14}(32.4, 12.91)
{\large \bfseries Model fitting} \\[.25cm]
Fitting is really hard to get right (Bayesian or ML).
If you are able to fit this model properly, the result is the empirical distribution of images.
You spent a lot of time just to get the empirical distribution back.
If you do not have an instance of every possible image in your training set, certain parameter must $\rightarrow \infty$, making fitting more complicated (shrink)
In reality it's practically impossible to have at least one of every possible image in your training set (large images, color scales, etc.)

>>>>

%%-----------------------------------------------
%%
%%Top right box
%%
\begin{textblock}{14}(32.4, 5.71)
{\large \bfseries Manageable (a.k.a. small) examples}
\begin{figure}
\centering
\includegraphics{images/degeneracy.pdf}
\includegraphics{images/instability.pdf}
\includegraphics{images/uninterpretability.pdf}
\label{fig:three_ways}
\caption{As the magnitude of $\boldsymbol \theta$ grows, so does the occurence of near-degeneracy, instability, and uninterpretability for RBMs of varying sizes.}
\end{figure}
\end{textblock}

%%-----------------------------------------------
%%
%%Middle right box
%%
\begin{textblock}{14}(32.4, 14)
{\large \bfseries Model fitting} \\[.25cm]
Fitting is really hard to get right (Bayesian or ML).
If you are able to fit this model properly, the result is the empirical distribution of images.
You spent a lot of time just to get the empirical distribution back.
If you do not have an instance of every possible image in your training set, certain parameter must $\rightarrow \infty$, making fitting more complicated (shrink)
In reality it's practically impossible to have at least one of every possible image in your training set (large images, color scales, etc.)
